A sensor grid approach for large scale acoustic monitoring

### 2017-08-22 paper/article.tex
fix ref

The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns. To better address those, the monitoring the acoustic environment in urban but also rural or wilderness areas is among other monitoring efforts an important matter. Fostering on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.

@@

The considered sensor network primarily aims at monitoring urban sound environment, that is, continuously assessing their content and impact on the population. In the literature, this is typically performed by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA. However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}. Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics. Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}.\\

\pa{En fait tu as aussi des indicateurs sur le spectre, le très utilisé CGS par exemple. En fait tu devrais peut-être t'arrêter à dire que il y a pleins d'indicateurs, mais ces indics donnent de l'info sur l'env. sonore dans sa globalité, mais pas sur les sources sonores en particulier. Pourtant les sources ont de la place sur l'appréciation du soundscape (et peut-être plus que des indics globaux, par exemple 50dB de voix humaine, c'est pas la même chose que 50dB d'oiseaux). Tu peux citer la tentative dans la publi avec Catherine où on calculait le TFSD4khz qui est bien corrêlé avec les oiseaux, mais ça ne remplacera pas une vrai detection de sources. }

A simple solution is the calculation of energetic indicators for the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ \pa{pour des périodes très courtes (fast or slow)} This measurement appears well-suited for this work's purpose: in addition to being an efficient descriptor \cite{torija2013}, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted.
 \pa{le spectrogramme en soit c'est pas un descripteur efficient, bcp trop d'info, par contre, tu as raison, avec lui on peut calculer la plupart des indicateurs cités et en plus sert pour faire de la reconnaissance. Tu peux aussi dire que du coup on fait l'impasse sur les Mel ou sur les indicateurs psychoacoustiques comme la Sonie ou le roughness. On en reparlera de vive voix si tu veux.}

@@

The recognition of sources of interest from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. However, the selection of relevant features is still an open debate. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, mel spectrograms and their cepstral-domain derivation, the mel-frequency cepstrum coefficients (MFCC), are the most recurrent. These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale.

@@

The technical constraints of size inherent to the studied setup make it impossible to transmit raw audio recordings \pa{and not wanted for privacy reason}. Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice. As mentioned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period. The resulting representation is also close to that of mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\

@@

\pa{desfois tu mets une majuscule à mel et desfois non...}

@@

Alternatively, we also implement the mel filterbank for comparison purposes, as the mel filterbank is the root representation of many state of the art classification algorithms. Mel spectrograms can thus be used as a baseline method to evaluate the relative performance of third-octave bands in sound event recognition.

@@

In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$. Huffman encoding is then computed with either a frame-specific symbol-code dictionary or a constant one generated from an entire dataset. A comparison of both methods is shown in Figure~\ref{fig:dict_comp}. For most short texture frame duration, we found the local Huffman algorithm to be much faster. In fact, encoding complexity is function of the amount of dictionary elements. If it is specific to a given data packet, then it does not need to contain every possible value. This gain seem to outweight the additional complexity induced by the need to transmit the result of the tree generation algorithm. Alternatively, short texture frames or single analysis windows can be encoded using one general dictionary to improve bitrate. Choosing between those two approaches is the result of a balance between requirements in terms of size and complexity.\\

@@

The decoding process is quite straightforward, as both Huffman and $\Delta$ compression are lossless and invertible directly. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.

@@

The main indicator of performance is the bitrate obtained at the output of the coder. The three varying factors studied are the data word size $q$, the number of bands and the effect of reducing time-resolution by averaging analysis frames. Figure~\ref{fig:bitrate_q} shows estimations of the output bitrate for different values of $q$. To match third-octave bands computation principle where a 125~ms analysis is mandatory, we averaged mel frames over time. Because we use the most common parameters, namely 23.2~ms window with 50\% overlap, the closest achievable rate considering simple averaging is 7.74 frames per second. Third-octave representation on 31 bands yielded an overall higher size than their mel equivalent, here estimated for 30 bands. It however compares with the 40-mel bands representation which is the most used features in literature. This higher bitrate is likely due to the distribution observed by the data prior to Huffman encoding.

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{figures/bitrate_qall.eps}
	\caption{Coder output bitrate as a function of quantization for third-octave and mel bands with 8 frames per second.}
	\label{fig:bitrate_q}
\end{figure}

A second set of parameters influences directly the time-frequency resolution of the analysis. By choosing a frame rate and number of bands, one can effectively control the size of periodically transmitted data. We evaluate the bitrate for 10 to 40 mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$. Results are shown in Figure~\ref{fig:bitrate_mel_avg}. As expected, the bitrate for a given word size $q$ can be modeled as a linear function of the representation dimensions for one second of analysis. Small variations are induced by data distributions on a per-frame level and their impact on the Huffman algorithm.

@@

The measurement error is computed for third-octave bands. Results are displayed in Figure~\ref{fig:error_m}. Only full-octave bands are shown for visibility. When computing the slow analysis, we found that applying overlap attenuated the error. This was not observed for fast analysis where the error was similar or higher with the use of overlapping frames. We propose to study the absolute error metric, as all experiments show a mean error close to zero.

@@

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[h]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/err_m_n.eps} 
        \caption{Noise extracts}
    \end{subfigure}
    \hfill
    \begin{subfigure}[h]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/err_m_u.eps} 
        \caption{Urban sounds recordings}
    \end{subfigure}
    \label{fig:error_m}
    \caption{Measurement error of third-octave bands over two-seconds recordings. The analysis of short frames has an effect on energy estimation at low frequencies. Framing is more impactful on signals where the energy is localized in frequency.}
\end{figure*}

@@

We also examine the additional error caused by the encoding steps after obtaining the desired data representation. The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits. However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data is in fact quantized on $2^{q-1}$ values. Since these measurements are already expressed in dB, the error $\varepsilon$ is:
\begin{equation*}
	\varepsilon = |x_q-x|
\end{equation*}
where $x_q$ and $x$ are the quantized and clean representations repectively. $x_q$ is given by:
\begin{equation*}
x_q(n) = \frac{\Delta_x}{2^{q-1}-1}\textrm{round}\left(\frac{(2^{q-1}-1)x(n)}{\Delta_x}\right), x\in \left[0, \Delta_x\right]
\end{equation*}
Figure~\ref{fig:error_q} shows an estimation of $\varepsilon$ as a function of $q$ for third-octave and mel bands. In both cases, the mean and standard deviation seem to decrease by a factor of 2 as $q$ increases. To explain this phenomenon, let us model $x$ as a uniform distribution such as $x\sim \textit{U}\{0, \Delta_x\}$. While this is not exact it matches our objective when using a logarithm to flatten given PDFs. The error $\varepsilon$ will follow a uniform distribution $U\sim \{0, \frac{\Delta_x}{2\times (2^{q-1}-1)}\}$. Therefore, the mean and standard deviation are:
\[
\begin{cases}
	\mu_\epsilon = \frac{\Delta_x}{4\times (2^{q-1}-1)}\\
	\sigma_\epsilon = \frac{1}{12}\frac{\Delta_x}{2\times (2^{q-1}-1)}
\end{cases}
\]
justifying the decaying ratio as $q$ increases. In practice, we assume that $\varepsilon = f(\Delta_x, \frac{1}{2^{q-1}-1})$ with the heterogeneity of the data's PDF inducing small variations.

@@

First, we observe the impact of quantization on classification accuracy. The models are trained on the most complete implemented representation, ie. 40 mel bands and no time averaging (85 frames per second). Figure~\ref{fig:class_mel_q} shows that this process yields equivalent accuracy for higher resolutions.\\

@@

The effect of changing the time-frequency resolution of the representation is presented in Table~\ref{T2}. Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively. However, we find that given our setup, reducing the number of analysis bands up to a given level most often does not induce a strong drop of performance. The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 mel bands only and a 4\% lower accuracy for 40. The latter result may be due to the low ability of the decision tree classifier to handle hugh dimensional features. Even if the difference is small, all other models perform best with 30 or 40 mel bands as a representation. Time decimation cn also be considered, as the original representation can be averaged and consistently yield a good classification accuracy. The loss of information can be considered negligible for FPS values as low as 20 or 10 depending on the method. Even below, classification accuracy only drops by one or a few percents. This means that we can effectively divide the data size by a factor of at most 10 without strongly affecting sound event recognition performance. It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\\

@@

We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of mel spectrograms. Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands. Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps mel spectrograms seen in Table~\ref{T2} for all classification schemes. In this table, equivalence of performance with respect to the best performing setting (in red) is depicted with a bold font evaluated using the following procedure. The null hypothesis that the subtraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance is evaluated using the paired-sample t-test at the 0.05 significance level. If the null hypothesis is not rejected, the setting is considered as equivalent in terms of performance to the best performing one. \\

@@

To further analyze both representations advantages, the confusion matrix is a reliable tool. It aims at providing information regarding class-by-class accuracy and misclassification rates. We thus compute these metrics for the SVM classifier, with predictions accumulated over the ten folds in test configuration. The analogous natures of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average. Both representations yield best results for the \textit{Gun shot} class with 88.2\% for third-octave cepstra and 86.6\% for mel cepstra. Their poorest accuracy is on the \textit{Air conditioning} class with 32.0\% and 38.1\% respectively. However, a noticeable difference between them is that on the log-frequency scale the bandwidth of mel filters narrows as frequency increases, while third-octave are evenly distributed. The effect of this can be seen between classes \textit{Drilling} and \textit{Jackhammer}. These sounds involve important low-frequency information which can generally differentiate them, leading third-octave descriptors to perform better. Conversely, using mel-based cepstra improves globally \textit{Air conditioning} recognition as most of its defining components are situated in higher frequencies.\\

@@

Objective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}}. The results of the perceptual test is evaluated using the average intelligibility score (AIS) given by the subjects and the ineligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance. Figure~\ref{fig:subj_int} presents the results of the perceptual test for the same encoder's settings.

@@

An audio encoding scheme have been described and motivated for use in a sensor grid approach to tackle the problem of large scale acoustic monitoring.

The proposed approach have the following benefits:
\begin{itemize}
	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.5dB) and thus:
	- respect the acoustics indicators which could be calculated from the spectrogram.
	- permits to perform the sound recognition with the same quality than directly from the spectrogram.
	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode
	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible.
\end{itemize}

>>>>

The spreading of urban areas and the growth of human population worldwide raised societal and environmental concerns. To better address those, the monitoring of the acoustic environment in urban but also rural or wilderness areas is among other monitoring efforts an important matter. Fostering on the recent development of low cost hardware acoustic sensors, we propose in this paper to consider a sensor grid approach to tackle this issue.

@@

The considered sensor network primarily aims at monitoring urban sound environment, that is, continuously assessing their content and impact on the population. In the literature, this is typically performed by measuring energetic acoustic indicators such as the equivalent sound pressure level $L_{eq}$ in dB SPL or its A-weighted equivalent $L_{Aeq}$ in dBA. However, while these indicators have proven to correlate well with perceptual evaluations for negative impact sound environments \cite{gozalo2015}, they are not sufficient to fully describe urban sound environments \cite{rychtarikova2013}. Many other variables can be derived to better account for previously implicit properties \cite{can2016} including percentile values or time dynamics. Studies have been conducted to select relevant subsets of descriptors in sound environment characterization \cite{can2015, brocolini2013, nilsson2007}. The mentionned $L_{eq}$ features are measured at periods of 0.125~ms or 1~s, respectively fast and slow as a convention.

Most measured or derived indicators describe the global urban soundscape and lack information on its composition. Sound sources recognition enables a more efficient understanding of soundscape properties. For instance, a bird song and traffic noise with the same energy can be perceived very differently. The analysis of sources within a sound environment is generally linked with spectral content \cite{ishiyama2000} and high temporal measurement resolutions. Other indicators can correlate with specific sound environment content \fg{cite Aumond/Lavandier TFSD} but do not achieve the same performances as a source detection scheme in characterizing soundscapes.

A solution is the calculation of spectral energetic indicators such as the 31 third-octave bands within the human audition range 20~Hz - 20~kHz.\\ Slow or fast third-octave bands measurement appears suitable for this work's purpose: in addition to being a relevant descriptor \cite{torija2013} for urban sound environment assessment, it allows for the computation of most cited indicators while representing reasonably small, fixed amounts of data to be transmitted. It additionnaly contains spectral information that can be used for source recognition tasks. However, as a tradeoff other representations such as Mel or Bark spectrograms, as well as psychoacoustical indicators cannot be precisely estimated.

@@

The recognition of sources of interest from audio streams has been the subject of extensive research in the past on speech \cite{anusuya2009}, music \cite{tzanetakis2002}, and lately more complex scenes in which the current work falls. Studied classification methods are diverse, ranging from time-dependant modeling with hidden markov models \cite{ntalampiras2014} to "bag-of-frames" approaches \cite{aucouturier2007, foggia2015}. Common architectures include learning-based classifiers such as support vector machines \cite{kumar2016}, Gaussian mixture models \cite{radhakrishnan2005} or neural networks \cite{salamon2017, piczak2015}. However, the selection of relevant features is still an open debate. The most used are certainly spectral \cite{khunarsal2013} or cepstral \cite{couvreur2004} representations of the signal. Among them, Mel spectrograms and their cepstral-domain derivation, the Mel-frequency cepstrum coefficients (MFCC), are the most recurrent. These representations effectively model the human cochlear response to sounds by grouping frequency components around critical bands in a logarithmic scale. While parameters are empirical and vary in the litterature, a reference implementation includes 23.2~ms analysis and a 40 Mel bands resolution. The resulting representations are generally more precise in time and frequency than in acoustic monitoring applications because it is a primordial factor for classification whereas acoustic indicators must be computed more accurately.

@@

The technical constraints of size inherent to the studied setup as well as privacy concerns make it impossible to transmit raw audio recordings. Following the considerations briefly exposed in the previous section, we conclude that third-octave bands are a reasonable choice. As mentioned, they provide advantages in both acoustic monitoring quality and reduced data volume per measurement period. The resulting representation is also close to that of Mel spectrograms, being just another filterbank transform with logarithmic frequency scaling.\\

@@

@@

Alternatively, we also implement the Mel filterbank for comparison purposes, as the Mel filterbank is the root representation of many state of the art classification algorithms. Mel spectrograms can thus be used as a baseline method to evaluate the relative performance of third-octave bands in sound event recognition.

@@

In the example shown here, the former is $H_{log} = 6.24~sh$ and the latter $H_{\Delta} = 3.54~sh$. Huffman encoding is then computed with either a frame-specific symbol-code dictionary or a constant one generated from an entire dataset. A comparison of both methods is shown in Figure~\ref{fig:dict_comp}. For most short texture frame duration, we found the local Huffman algorithm to be much faster. In fact, encoding complexity is function of the amount of dictionary elements. If it is specific to a given data packet, then it does not need to contain every possible value. This gain seems to outweight the additional complexity induced by the need to transmit the result of the tree generation algorithm. Alternatively, short texture frames or single analysis windows can be encoded using one general dictionary to improve bitrate. Choosing between those two approaches is the result of a balance between requirements in terms of size and complexity.\\

@@

The decoding process is quite straightforward, as both Huffman and $\Delta$ compressions are lossless and directly invertible. The entire coder scheme is summarized in Figure~\ref{fig:scheme}.

@@

The main indicator of performance is the bitrate obtained at the output of the coder. The three varying factors studied are the data word size $q$, the number of bands and the effect of reducing time-resolution by averaging analysis frames. Figure~\ref{fig:bitrate_q} shows estimations of the output bitrate for different values of $q$. To match third-octave bands computation principle where a 125~ms analysis is mandatory, we averaged Mel frames over time. Because we use the most common parameters, namely 23.2~ms window with 50\% overlap, the closest achievable rate considering simple averaging is 7.74 frames per second. Third-octave representation on 31 bands yielded an overall higher size than their Mel equivalent, here estimated for 30 bands. It however compares with the 40-Mel bands representation which is the most used features in literature. This higher bitrate is likely due to the distribution observed by the data prior to Huffman encoding.

\begin{figure}[htbp]
	\centering
		\includegraphics[width=\columnwidth]{figures/bitrate_qall.eps}
	\caption{Coder output bitrate as a function of quantization for third-octave and Mel bands with 8 frames per second.}
	\label{fig:bitrate_q}
\end{figure}

A second set of parameters influences directly the time-frequency resolution of the analysis. By choosing a frame rate and number of bands, one can effectively control the size of periodically transmitted data. We evaluate the bitrate for 10 to 40 Mel bands and a frame rate from 2 to 10 per second, with fixed $q = 8$. Results are shown in Figure~\ref{fig:bitrate_mel_avg}. As expected, the bitrate for a given word size $q$ can be modeled as a linear function of the representation dimensions for one second of analysis. Small variations are induced by data distributions on a per-frame level and their impact on the Huffman algorithm.

@@

The measurement error is computed for third-octave bands. Results are displayed in Figure~\ref{fig:errorm}. Only full-octave bands are shown for visibility. When computing the slow analysis, we found that applying overlap attenuated the error. This was not observed for fast analysis where the error was similar or higher with the use of overlapping frames. We propose to study the absolute error metric, as all experiments show a mean error close to zero.

@@

\begin{figure*}[h!]
    \centering
    \begin{subfigure}[h]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/err_m_n.eps}
        \caption{Noise extracts}
    \end{subfigure}
    \hfill
    \begin{subfigure}[h]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/err_m_u.eps}
        \caption{Urban sounds recordings}
    \end{subfigure}

    \caption{Measurement error of third-octave bands over two-seconds recordings. The analysis of short frames has an effect on energy estimation at low frequencies. Framing is more impactful on signals where the energy is localized in frequency. \label{fig:errorm}}
\end{figure*}

@@

We also examine the additional error caused by the encoding steps after obtaining the desired data representation. The only lossy operation applied is quantization, which is defined by an output word size $q$ in bits. However, it corresponds to the word size \textit{after} $\Delta$-compression, meaning that the data is in fact quantized on $2^{q-1}$ values. Since these measurements are already expressed in dB, the error $\varepsilon$ is:
\begin{equation*}
	\varepsilon = |x_q-x|
\end{equation*}
where $x_q$ and $x$ are the quantized and clean representations repectively. $x_q$ is given by:
\begin{equation*}
x_q(n) = \frac{\Delta_x}{2^{q-1}-1}\textrm{round}\left(\frac{(2^{q-1}-1)x(n)}{\Delta_x}\right), x\in \left[0, \Delta_x\right]
\end{equation*}
Figure~\ref{fig:error_q} shows an estimation of $\varepsilon$ as a function of $q$ for third-octave and Mel bands. In both cases, the mean and standard deviation seem to decrease by a factor of 2 as $q$ increases. To explain this phenomenon, let us model $x$ as a uniform distribution such as $x\sim \textit{U}\{0, \Delta_x\}$. While this is not exact it matches our objective when using a logarithm to flatten given PDFs. The error $\varepsilon$ will follow a uniform distribution $U\sim \{0, \frac{\Delta_x}{2\times (2^{q-1}-1)}\}$. Therefore, the mean and standard deviation are:
\[
\begin{cases}
	\mu_\epsilon = \frac{\Delta_x}{4\times (2^{q-1}-1)}\\
	\sigma_\epsilon = \frac{1}{12}\frac{\Delta_x}{2\times (2^{q-1}-1)}
\end{cases}
\]
justifying the decaying ratio as $q$ increases. In practice, we assume that $\varepsilon = f(\Delta_x, \frac{1}{2^{q-1}-1})$ with the heterogeneity of the data's PDF inducing small variations.

@@

First, we observe the impact of quantization on classification accuracy. The models are trained on the most complete implemented representation, ie. 40 Mel bands, 23.2~ms, 50\% overlap and no time averaging (85 frames per second). Figure~\ref{fig:class_mel_q} shows that this process yields equivalent accuracy for higher resolutions.\\

@@

The effect of changing the time-frequency resolution of the representation is presented in Table~\ref{T2}. Similarly to baseline results, the random forest and SVM classifiers are the higher performing systems at $0.69\pm 0.06$ and $0.68\pm 0.04$ respectively. However, we find that given our setup, reducing the number of analysis bands up to a given level most often does not induce a strong drop of performance. The performance of the decision tree classifier is a good example of this behavior, with best performances for 10 Mel bands only and a 4\% lower accuracy for 40. The latter result may be due to the low ability of the decision tree classifier to handle hugh dimensional features. Even if the difference is small, all other models perform best with 30 or 40 Mel bands as a representation. Time decimation cn also be considered, as the original representation can be averaged and consistently yield a good classification accuracy. The loss of information can be considered negligible for FPS values as low as 20 or 10 depending on the method. Even below, classification accuracy only drops by one or a few percents. This means that we can effectively divide the data size by a factor of at most 10 without strongly affecting sound event recognition performance. It also provides us with a preliminary confirmation of the possibility for "fast"-sampled third-octave bands cepstra to match  MFCC performances.\\

@@

We now compare the efficiency of third-octave bands at characterizing urban soundscapes to that of Mel spectrograms. Following the previous discussions, the classification task is run on corresponding cepstra with a fixed 8 frames per second and 31 bands. Figure~\ref{fig:class_tob_q} displays similar results to the 40 bands, 8 fps Mel spectrograms seen in Table~\ref{T2} for all classification schemes. In this table, equivalence of performance with respect to the best performing setting (in red) is depicted with a bold font evaluated using the following procedure. The null hypothesis that the subtraction of the two compared distribution (the distribution of the setting we consider minus the distribution of the best performing one) comes from a normal distribution with mean equal to zero and unknown variance is evaluated using the paired-sample t-test at the 0.05 significance level. If the null hypothesis is not rejected, the setting is considered as equivalent in terms of performance to the best performing one. \\

@@

To further analyze both representations advantages, the confusion matrix is a reliable tool. It aims at providing information regarding class-by-class accuracy and misclassification rates. We thus compute these metrics for the SVM classifier, with predictions accumulated over the ten folds in test configuration. The analogous natures of the two descriptors is highlighted by close one-versus-one differentiation performances, with a slightly lower accuracy for third-octave bands on average. Both representations yield best results for the \textit{Gun shot} class with 88.2\% for third-octave cepstra and 86.6\% for Mel cepstra. Their poorest accuracy is on the \textit{Air conditioning} class with 32.0\% and 38.1\% respectively. However, a noticeable difference between them is that on the log-frequency scale the bandwidth of Mel filters narrows as frequency increases, while third-octave are evenly distributed. The effect of this can be seen between classes \textit{Drilling} and \textit{Jackhammer}. These sounds involve important low-frequency information which can generally differentiate them, leading third-octave descriptors to perform better. Conversely, using Mel-based cepstra improves globally \textit{Air conditioning} recognition as most of its defining components are situated in higher frequencies.\\

@@

Subjective intelligibility metrics are then computed for the encoder's settings under evaluation and compared to the results of the perceptual test \footnote{Decoded speech utterances for various conditions can be listened to at \url{https://felixgontier.github.io/cense-coder/}}. The results of the perceptual test is evaluated using the average intelligibility score (AIS) given by the subjects and the intelligibility ratio (IR) computed as the number of correctly transcribed words versus the number of words in the spoken utterance. Figure~\ref{fig:subj_int} presents the results of the perceptual test for the same encoder's settings.

@@

An audio encoding scheme has been described and motivated for use in a sensor grid approach to tackle the problem of large scale acoustic monitoring.

The proposed approach has the following benefits:
\begin{itemize}
	\item precision: the impact of the quantization step for 8 bits codewords is found to be very small (< 0.5dB) and thus:
	- respect the acoustics indicators which could be calculated from the spectrogram.
	- permits to perform the sound recognition with the same quality than directly from the spectrogram.
	\item efficiency: for fast and slow modes, the bitrate is respectively about 1.4~kbps and 0.4~kbps for the high precision mode
	\item privacy: at all operating modes, the reverted audio signal is found to be inintelligible.
\end{itemize}
